---
title: "HW5"
author: "Emma"
date: "2023-03-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Team Names: Emma Podlich & Ryan Corydon
Link to Github Repository: https://github.com/epodlich/lab2


##Import Data

```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```

## Question Set 1

What is the overall number of chocolate bars rated?

```{r}

```

How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r}

```

## Question Set 2

For each of the questions below provide at least one graphic as a basis for your answer.

How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.

```{r}

```

Do ratings depend on the cocoa percentage of a chocolate bar?

```{r}

```

How do ratings compare across different company locations? Focus on the three locations with the most ratings:

```{r}

```

## Our Own Questions

Question 1: Emma

```{r}

```

Conclusions:

Question 2: Ryan

```{r}

```

Conclusions:

## Workflow

