---
title: "HW5"
author: "Emma & Ryan"
date: "2023-03-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Team Names: Emma Podlich & Ryan Corydon

Link to Github Repository: https://github.com/epodlich/lab2


## Import Data

```{r}
library(ggplot2)
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```

## Question Set 1

#### What is the overall number of chocolate bars rated?

The overall number of chocolate bars rated is 1852.

```{r}
summary(choco)
```

#### How does the number of ratings depend on the year? Draw a bar chart of the number of reports. 

As years increased the number of ratings generally increased as well. From 2005 until 2017 we can see that 2015 was the best year for movies and 2005 was the worst. Shockingly, after 2015 there is a steady decrease in the amount of movies rated.

```{r}
ggplot(choco, aes(x = Review.Date)) + 
  geom_bar(aes(weight= Rating)) 
```

## Question Set 2

### For each of the questions below provide at least one graphic as a basis for your answer.


#### How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any. 

Looking at the histogram there seems to be two outliers, a rating with a score of 1 and a rating with a score of 5. The histogram shows the most common ratings are between 2.5 and 4 with the highest being around 3.5.

```{r}
ggplot(choco, aes(x = Rating)) + 
  geom_histogram(binwidth=0.25) +
  ggtitle("binwidth = 0.25")
```

#### Do ratings depend on the cocoa percentage of a chocolate bar?

Looking at the scatterplot, we can conclude that ratings do not depend on cocoa percentage. As rating goes increase, cocoa percentage does not either increase or decrease making it an uneven distribution. There is an outlier with a rating of five and the percentage of cocoa is on 70.

```{r}
ggplot(data = choco, aes(x = Rating, y = Cocoa.Pct)) + geom_point() + geom_jitter()

```

#### How do ratings compare across different company locations? Focus on the three locations with the most ratings:

The ratings across the different company locations all have about the same median being around a rating of 3.25 and they have about the same maximum rating of 4. However, Canada has the highest 3rd quartile of about 3.75 while both the US and France have 3rd quartiles around 3.5. Also, the 1st quartile of the US is about 2.75 while the 1st quartiles for both France and Canada are about 3. The minimum ratings are the same for the US and Canada with values being around 2 while France's minimum is about 2.5. There is an outlier in the US of about 1.5 and two outliers in France of about 1.5 and 2. Overall, the ratings are pretty similar across the different company locations.

```{r}
choco.country = dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))

ggplot(choco.country, aes(x =Company.Location, y = Rating)) + geom_boxplot() + coord_flip()
```

## Our Own Questions

#### Question 1: Emma

How does the Review Date relate to the percentage of cocoa in the chocolate bars? More specifically, are there certain years where a certain percentage of cocoa in the chocolate bars was more popular?

```{r}
ggplot(choco, aes(x = Review.Date, y = Cocoa.Pct)) + 
  geom_point() + geom_jitter() 

ggplot(choco.country, aes(x = Cocoa.Pct)) + geom_boxplot() + facet_wrap(~Review.Date)
```

Conclusions: 

The review date does not appear to be related to the cocoa percent according to this scatter plot. The chocolate bar companies did not have years where certain cocoa percentages were the more popular. There don't appear to be any outliers in the scatter plot either.

The review date does not appear to be too related to the cocoa percent according to the box plots. The median percentage in all of the years appears to be around 70%. There are a couple outliers in each box plot; most notably there are about 10 in both years 2012 and 2013. However, there doesn't appear to be certain years where there is a distinct popular cocoa amount in the chocolate bars. Likely, companies stay around the 70% cocoa marker because that is what sells best.


#### Question 2: Ryan

The question I want to investigate is the distribution of cocoa percentage within the total number of chocolate bars.

```{r}
ggplot(choco, aes(x = Cocoa.Pct)) + 
  geom_histogram(binwidth=5) +
  ggtitle("binwidth = 5")
```

Conclusions: Through this histogram it can be concluded that most chocolate bars have a cocoa percentage of 70. I can assume the higher the percentage the more richer and sweeter the chocolate bar is. Meaning a bar with 100% cocoa probably does not taste very good. There is an outlier with a few bars that have 100% cocoa in them, as well there is a chocolate bar with only 42% cocoa.

## Workflow

The workflow of this homework assignment went pretty well. We began by creating an outline for this assignment which consisted of the questions that needed to be answered along with R code chunks below each question for writing the code to plot. Then, we both went through and answered the questions that we felt the most confident on. Next, we checked each others work to see if their conclusions and plots made sense. We also discussed possible questions that we would like to explore more and each chose one of the options we created in order to dive deeper into that topic by creating both plots and conclusions. Overall, the flow of the assignment and using github to collaborate went well.
